Hydras \& Co.

### 2022-02-16 doc/gaia-chapter.tex
first version of chapter 10

\chapter{Gaia and the hydras (experimental)}
\index{coq}{Plug-ins!Gaia}

@@

\section{Importing a theorem from \gaia}
The \texttt{Gaia} library already contains a proof that the multiplication of ordinals less than $\epsilon_0$ is associative.
\emph{From~\href{https://github.com/coq-community/gaia/blob/master/theories/ssete9.v}{gaia.ssete9.v}}

@@

@@

\inputsnippets{GCanon/g2hCanonRw}
\inputsnippets{GCanon/gcanonLt}
\inputsnippets{GCanon/glimitCanonSNotZero}
\inputsnippets{GCanon/gcanonLimitV2}
\inputsnippets{GCanon/gcanonLimitMono}
\inputsnippets{GCanon/gcanonLimitOf}

The functions $F_\alpha$ are described in Section~\vref{sect:wainer}. The symbol \texttt{F\_} has type \texttt{E0 -> nat -> nat},
where \texttt{E0} is the type of well formed ordinal terms less than $\epsilon_0$.
\subsubsection{Well-formed ordinal terms}

@@

@@

Mainly by rewriting, we import a few properties of the $F_\alpha$s.

\inputsnippets{T1Bridge/MonoDef, GF_alpha/FAlphaProps}.

>>>>

\chapter{Gaia and the hydras (experimental)}
\index{coq}{Plug-ins!Gaia}
\label{gaia-chapter}

@@

\section{Importing a theorem from \gaia}
The \texttt{Gaia} library already contains many lemmas about
ordinal arithmetic. In this section, we give two examples of
porting such a lemma to \HydrasLib' vocabulary.

\subsection{Associativity of ordinal multiplication (below \texorpdfstring{$\epsilon_0$}{epsilon\_0})}
\gaia already contains a proof that the multiplication of ordinals less than $\epsilon_0$ is associative.
\emph{From~\href{https://github.com/coq-community/gaia/blob/master/theories/ssete9.v}{gaia.ssete9.v}}

@@

 \subsection{Right Distributivity, etc.}
 Likewise, we prove almost for free that ordinal multiplication is right distributive over addition (with \HydrasLib' definitions).

 \inputsnippets{GaiaToHydra/distributivity}.

We plan to automatize the most as possible this transfer of lemmas in this direction.

@@

\subsection{A type for well-formed ordinal terms}

@@

\inputsnippets{GCanon/g2hCanonRw}
\inputsnippets{GCanon/gcanonLt}
\inputsnippets{GCanon/glimitCanonSNotZero}
\inputsnippets{GCanon/gcanonLimitMono}

Let us recall \gaia's definition of $\omega$-limit.

\inputsnippets{nfwfgaia/LimitV2Def, nfwfgaia/LimitOFDef}

We adapt theorems from \href{../theories/html/hydras.Epsilon0.Canon.html}%
{\texttt{hydras.Epsilon0.Canon}} to \gaia's vocabulary.

\inputsnippets{GCanon/gcanonLimitStrong}
\inputsnippets{GCanon/gcanonLimitV2}
\inputsnippets{GCanon/gcanonLimitOf}

The functions $F_\alpha$ are described in Section~\vref{sect:wainer}. The symbol \texttt{F\_} has type \texttt{E0 -> nat -> nat},
where \texttt{E0} is the type of well formed ordinal terms less than $\epsilon_0$.

@@

The following definitions adapt \HydrasLib' to \ssreflect's 
definitions of $<$ and $\leq$ on \texttt{nat}.

\inputsnippets{T1Bridge/MonoDef}

By rewriting, we import a few lemmas from
~\href{../theories/html/hydras.Epsilon0.F_alpha.html}{Epsilon0.F\_alpha}.

\inputsnippets{GF_alpha/FAlphaProps}

With the same technique, we prove that if
$\alpha\geq\omega$, then $F_\alpha$ is not primitive recursive.

\inputsnippets{GF_alpha/FAlphaNotPR}

### 2022-02-16 doc/part-hydras.tex
first version of chapter 10

>>>>

\subsection*{Compatibility with \gaia\cite{Gaia} (in progress)}
The \gaia project~\cite{Gaia} by Jos\'e Grimm aimed to formalize mathematics in \coq  in
the style of Nicolas Bourbaki. It contains many definitions and results about ordinal numbers. In Chapter~\ref{gaia-chapter}, we present some modules which allow \HydrasLib' users to apply lemmas proven in \gaia, and vice versa.
